`gosset`: An R package for analysis and synthesis of ranking data in agricultural

### 2022-06-25 inst/paper/paper.Rmd
update manuscript

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural
  experimentation'
abstract: null
output:
  word_document:
  pdf_document:
    fig_caption: yes
    number_sections: no
    keep_tex: no
  reference_docx: paper_template_format.docx
latex_engine: pdflatex
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: citationstyle.csl
header-includes:
- \usepackage{pdfpages}
- \usepackage{caption}
- \usepackage{xcolor}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{font=small}
---

>>>>

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural
  experimentation'
abstract: null
output:
  word_document:
  pdf_document:
    fig_caption: yes
    number_sections: no
    keep_tex: no
latex_engine: pdflatex
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
csl: citationstyle.csl
header-includes:
- \usepackage{pdfpages}
- \usepackage{caption}
- \usepackage{xcolor}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{font=small}
---
